### 2019-12-12 Statistical Methods/04_probability.rmd
statistical methods
statistical methods
statistical methods, ch4
statistical methods, ch4

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

For a binomial with n = 10 and p = .4, determine:

a.) $P(0)$

```{r, echo = T}
dbinom(0, size = 10, prob = .4)
```

b.) $P(X \le 3)$

```{r, echo = T}
pbinom(3, size = 10, prob = .4)
```

c.) $P(X < 3)$

```{r, echo = T}
pbinom(2, size = 10, prob = .4)
```

d.) $P(X > 4)$

```{r, echo = T}
1 - pbinom(4, size = 10, prob = .4)
```

e.) $P(2 \le X \le 5)$

```{r, echo = T}
pbinom(5, size = 10, prob = .4) - pbinom(1, size = 10, prob = .4)
```

For a binomial with n = 15 and p = 0.3, determine.

a.) $P(0)$

```{r, echo = T}
dbinom(x = 0, prob = .3, size = 15)
```

b.) $P( X \le 3 )$

```{r, echo = T}
pbinom( q = 3, prob = .3, size = 15)
```

c.) $P(X < 3)$

```{r, echo = T}
pbinom(2, size = 15, prob = .3)
```

d.) $P(X > 4)$

```{r, echo = T}
pbinom(4, size = 15, prob = .3, lower.tail = F)
```

e.) $P(2 \le X \le 5)$

```{r, echo = T}
pbinom(5, size = 15, prob = .3) - pbinom(1, size = 15, prob = .3)
```

For a binomial with n = 15, p = 0.6 determine the probability of exactly 10 successes.

```{r, echo = T}
dbinom(10, size = 15, prob = .6)
```

For a binomial with n = 7 and p = 0.35, what is the probability of exactly 2 successes?

```{r, echo = T}
dbinom(2, size = 7, p = .35)
```

For a binomial with n = 18 and p = 0.6, determine the mean, variance of X, the total number of successes.

```{r, echo = T}
n <- 18
p <- 0.6
q <- 1 - p

mu <- n * p
variance <- mu * q

For a binomial with n = 22 and p = .2, determine the mean and variance of X, the total number of successes.

```{r, echo = T}
n <- 22
p <- .2
q <- 1 - p

mu <- n * p
variance <- mu * q
```

For a binomial with n = 20 and p = .7, determine the mean and variance of $\hat{p}$, the proportion of observed success.

```{r, echo = T}
n <- 20
p <- .7
q <- 1 - p

mu <- n * p
variance <- mu * q
```

For a binomial with n = 30 and p = 0.3, determine the mean and variance of $\hat{p}$.

```{r, echo = T}
n <- 30
p <- .3
q <- 1 - p

phat <- p / n
variance <- p*q / n
```

$\hat{p} = `r phat`$, $\sigma^2 = `r variance`$

### 4.32

For a binomial with n = 10 and p = 0.8, determine:

```{r, echo = T}
n <- 10
p <- 0.8
q <- 1 - p

variance <- p*q / n
```

a.) the probability that $\hat{p}$ is less than or equal to 0.7.

@@

b.) the probability that $\hat{p}$ is greater than or equal to 0.8.

@@

c.) the probability that $\hat{p}$ is exactly equal to 0.8.

@@

A coin is rigged so that when it is flipped, the probability of a head is 0.7. If the coin is flipped three times, which is the more likely outcome, exactly three heads or two heads and a tail?

@@

dbinom(3, 3, .7) # 3 heads

dbinom(2, 3, .7) # 2 heads 1 tail

@@

_Two heads, 1 tail._

@@

Imagine that the probability of heads when flipping a coin is given by the binomial probability function with p = 0.5.

If you flip the coin nine times and get nine heads, what is the probability of a head on the 10th flip?

```{r, echo = T}
# independent events.
dbinom(1, 1, .5)
```

The Department of Agriculture of the United States reports that 75% of all people who invest in the futures market lose money. Based on the binomial probability function, with n = 5, determine:

a.) the probability that all 5 lose money.

$P(x) = 0$

```{r, echo = T}
dbinom(5, size = 5, prob = .75)
```

b.) the probability that all five make money.

```{r, echo = T}
dbinom(5, size = 5, prob = .25)

@@

c.) the probability that at least two lose money.

```{r, echo = T}
pbinom(q = 3, size = 5, prob = .25)
```

@@

If for a binomial distribution p = 0.4 and n = 25, determine:

a.) $P(X < 11)$

b.) $P(X \le 11)$

c.) $P(X > 9)$

d.) $P(X \ge 9)$

@@

In the previous problem, determine the mean of X, the variance of X, the mean of $\hat{p}$, and the variance of $\hat{p}$.

@@

Given that Z has a standard normal distribution, determine:

a.) $P(Z \ge 1.5)$

b.) $P(Z \le -2.5)$

c.) $P(Z < -2.5)$

d.) $P(-1 \le Z \le 1)$

@@

If Z has a standard normal distribution, determine:

a.) $P(Z \le 0.5)$

b.) $P(Z > 1.25)$

c.) $P(-1.2 \le Z \le 1.2)$

d.) $P(-1.8 \le Z \le 1.8)$
